Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-02-02 R0V0.tex
Start the first paragraph

\mypara Over the years, methods for the design of distributed controllers for large-scale systems have developed different techniques, according to the vector field that describes the system structure. For linear systems, controller design problems are often translated in terms of optimization.

>>>>

\mypara Over the years, the improvements on distance communication and cheaper computation platform have allowed the development of large-scale interconnected systems such as smart grids, smart sensor networks, smart manufacturing plants and intelligent transportation systems. One of the main characteristic of these systems is the capacity of being autonomous. Most of current controller algorithms written to render technologies automatic is based on the assumption that the system will operate ``near'' to a prescribed set point. In other words, the system will designed fixed behavior. This assumption imposes severe limitations for system, as large excursions are not allowed, in general. For instance, large variations on smart grids are not allowed and manufacturing plants tend to synthesize only a fixed range of goods. To render these systems more flexible, i.e., allowing large excursions a controller algorithm that takes into account a more complex behavior is needed.

\mypara In terms of mathematical systems theory, the difference between a system operating in a set point and operating in a much larger region lies in the type of equations that describes the system behavior. For the former, the system is described by linear equation while, for the latter, by a nonlinear one. 
\todo[inline]{Continue with difficulties to design nonlinear controller.}
Methods for the design of distributed controllers for large-scale systems have developed different techniques, according to the vector field that describes the system structure. For linear systems, controller design problems are often translated in terms of optimization.
